\section{Problem statement}

\begin{frame}{Problem statement}

One level evacuation model well known \\
$\rightarrow$  Multilevel? i.e. ETH-CAB?\\
Goal: Tool to simulate evacuation in a given multilevel building.\\
Requirements of solution
\begin{itemize}
\item Efficient
\item Flexible
\item Realistic
\end{itemize}

\end{frame}


\section{Model}

\begin{frame}{Social Force Model}
The social force model, introduced by Helbling is an agent based model to simulate pedestrians behaviour.\\
Described forces
\begin{itemize}
\item Desired Direction Force
\item Interaction Force
\item Wall Force
\end{itemize}
\end{frame}

\begin{frame}{Desired Direction}
Every agent targets the shortest possible path with a desired velocity to the closest exit.
\begin{equation*}
f_{D}=\frac{v_{i}^{0}(t)\mathbf{e}_{i}^{0}(t)-\mathbf{v}_{i}(t)}{\tau_{i}}
\end{equation*}
\begin{itemize}
\item $v_{i}^{0}(t)\mathbf{e}_{i}^{0}(t)$: Desired velocity and direction
\item $\mathbf{v}_{i}(t)$: Current velocity
\end{itemize}
\end{frame}

\begin{frame}{Repulsive Interaction Force}
All agents interact with each other when they get close. Prevent agents from penetrating.
\begin{equation*}
f_{ij}=\left\{A_{i}exp[(r_{ij}-d_{ij})/B_{i}]+kg(r_{ij}-d_{ij})\right\}\mathbf{n}_{ij}+\kappa g(r_{ij}-d_{ij})\triangle v_{ji}^t\mathbf{t}_{ij}
\end{equation*}
\begin{itemize}
\item $A_{i}exp[(r_{ij}-d_{ij})/B_{i}]\cdot\mathbf{n}_{ij}$: Exponentially increasing force with an repulsive effect, the closer agents get to each other.
\item The other two summands contribute only to the force when agents overlap
\end{itemize}
\end{frame}

\begin{frame}{Wall Force}
The wall force fulfills the same purpose as the repulsive interaction force. Though prevents agents from penetrating walls.
\begin{multline*}
f_{iW}=\left\{A_{i}exp[(r_{i}-d_{iW})/B_{i}]+kg(r_{i}-d_{iW})\right\}\mathbf{n}_{iW}\\-\kappa g(r_{i}-d_{iW})(\mathbf{v}_{i}\cdot\mathbf{t}_{iW})\mathbf{t}_{iW}
\end{multline*}
\begin{itemize}
\item Same as the repulsive interaction force between agents
\end{itemize}
\end{frame}

\section{Implementation}

\begin{frame}{Implementation}
\begin{itemize}
 \item General config files suitable for many buildings
 \item Color-coded bitmaps of floor plans
 \item All formulas implemented as proposed by Dirk Helbling
 \item Custom functions written in \textit{C}
 \begin{itemize}
  \item Fast Sweeping for path finding and wall interaction
  \item 2D Range Tree for efficient inter-agent force computation
  \item Bilinear interpolation to replace \textit{MATLAB}'s built in interp2()
 \end{itemize}
 \item Easily extendable code
\end{itemize}
\end{frame}


\section{Demonstration}

\begin{frame}{Video demonstration}
$\rightarrow$ config1\_frame.avi
\end{frame}


\section{Discussion}

\begin{frame}{Discussion}
\begin{itemize}
	\item Model works as expected
		\begin{itemize}
			\item agents take shortest path towards exit
			\item agents don't intersect with wall \& each other
			\item formation of crowds
		\end{itemize}
	\item Stairs \& exits are bottlenecks
	\item Simplified model: improvements possible
		\begin{itemize}
			\item add 'intelligence' to the agents
			\item add a 'panic factor'
			\item use different agent velocities
		\end{itemize}
\end{itemize}
\end{frame}


\section{Questions}

\begin{frame}{Questions}
	\begin{itemize}
		\item Thanks for your attention!
		\item Questions ?
	\end{itemize}
\end{frame}
